### 2017-04-22 chapters/01-intro.tex
Add folders

The second chapter offers a rational choice account for the \textit{jogo do bicho}, or the `animal game', possibly the largest illegal gambling game in the world. The lottery has been running for over 120 years and according to estimations of Fundação Getúlio Vargas, a Brazilian think tank, it profits up to 800 million dollars per year.\footnote{See \url{http://goo.gl/9kNeX8} and \url{http://goo.gl/8FSAZl} (in Portuguese). Access: April 2017} The \emph{jogo do bicho} has exerted a significant impact on the Brazilian society. The lottery has been a major sponsor of the Carnival Parade in Rio de Janeiro, which is among the world's most famous popular festivals, and it has remained an important driver of state corruption in the country \citep{bezerra2009mecenato,chazkel2011laws,da1999aguias,labronici2012paratodos,magalhaes2005ganhou,soares1993jogo}. I investigate the institutions that have caused the \emph{jogo do bicho}'s notable growth and long-term survival outside the boundaries of the Brazilian law. I show how \textit{bicheiros} or bookmakers promote social order, solve information asymmetries, and reduce negative externalities via costly signalling and the provision of club goods. I also explain the emergence of the informal rules that govern the game as well as their enforcement mechanisms.

>>>>

The second chapter offers a rational choice account for Brazil's \textit{jogo do bicho}, or the `animal game', possibly the largest illegal gambling game in the world. The lottery has been running for over 120 years and according to estimations of Fundação Getúlio Vargas, a Brazilian think tank, it profits up to 800 million dollars per year.\footnote{See \url{http://goo.gl/9kNeX8} and \url{http://goo.gl/8FSAZl} (in Portuguese). Access: April 2017} The \emph{jogo do bicho} has exerted a significant impact on the Brazilian society. The lottery has been a major sponsor of the Carnival Parade in Rio de Janeiro, which is among the world's most famous popular festivals, and it has remained an important driver of state corruption in the country \citep{bezerra2009mecenato,chazkel2011laws,da1999aguias,labronici2012paratodos,magalhaes2005ganhou,soares1993jogo}. I investigate the institutions that have caused the \emph{jogo do bicho}'s notable growth and long-term survival outside the boundaries of the Brazilian law. I show how \textit{bicheiros} or bookmakers promote social order, solve information asymmetries, and reduce negative externalities via costly signalling and the provision of club goods. I also explain the emergence of the informal rules that govern the game as well as their enforcement mechanisms.

### 2017-04-22 chapters/02-synth.tex
Add folders

In this paper, I employ the synthetic control method (henceforth SCM) to approximate this experimental ideal and measure the total causal effect of post-1999 public policies on São Paulo homicide rates. The method consists of creating an artificial counterfactual to estimate the impact of a given intervention on a unit of interest. SCM has gained widespread acceptance in many fields, having been successfully applied in political science \citep{abadie2014, montalvo2011}, economics \citep{billmeier2013, coffman2012, jinjarak2013}, education studies \citep{hinrichs2012}, and public health science \citep{heim2014}. However, SCM has rarely, if ever, been used to evaluate homicide prevention strategies in São Paulo, despite being a useful tool for this particular type of question. SCM was specifically designed for situations where there is only one treated unit of interest, no readily-available counterfactual, and no certainty as to whether the treated and the control units follow parallel trends after the intervention \citep{abadie2003, abadie2010, abadie2014}. Moreover, SCM also has some of the desirable properties of other popular causal inference tools such as differences-in-differences \citep{angrist2008mostly, bertrand2004much} and matching estimators \citep{dehejia2002propensity, ho2007matching, rubin1973matching, stuart2010matching}.

@@

It seems that the influence of the PCC on physical violence has been overstated. It is unlikely that the PCC -- which is underfunded for its size\footnote{A Parliamentary Commission of Inquiry has stated that the PCC earns about 16 million Brazilian Reals per month, which amounts to approximately 60 million US dollars per year (see: \url{http://goo.gl/FwhPa3} (in Portuguese). Access: July 2016. Given the size of the organisation and its undisputed position as the leading crime syndicate in São Paulo, the figures are rather small. As a comparison, Mexico's Sinaloa Cartel profits about 3 billion dollars per year, a sum comparable to the annual earnings of Netflix or Facebook. See: \url{http://nyti.ms/1B09qyV}. Access: July 2016.} -- could have achieved such deep penetration into society and lowered the violence levels across all population groups in the whole state.

>>>>

In this paper, I employ the synthetic control method (henceforth SCM) to approximate this experimental ideal and measure the total causal effect of post-1999 public policies on São Paulo homicide rates. The method consists of creating an artificial counterfactual to estimate the impact of a given intervention on a unit of interest. SCM has gained widespread acceptance in many fields, having been successfully applied in political science \citep{abadie2014, montalvo2011}, economics \citep{billmeier2013, coffman2012, jinjarak2013}, education studies \citep{hinrichs2012}, and public health science \citep{heim2014}. However, SCM has rarely, if ever, been used to evaluate homicide prevention strategies in São Paulo, despite being a useful tool for this particular type of question. SCM was specifically designed for situations where there is only one treated unit of interest, no readily-available counterfactual, and no certainty as to whether the treated and the control units follow parallel trends after the intervention \citep{abadie2003, abadie2010, abadie2014}. Moreover, SCM also has some of the desirable properties of popular causal inference tools such as differences-in-differences \citep{angrist2008mostly, bertrand2004much} and matching estimators \citep{dehejia2002propensity, ho2007matching, rubin1973matching, stuart2010matching}.

@@

It seems that the influence of the PCC on physical violence has been overstated. It is unlikely that the PCC -- which is underfunded for its size\footnote{A Parliamentary Commission of Inquiry has stated that the PCC earns about 16 million Brazilian Reals per month, which amounts to approximately 60 million US dollars per year. See: \url{http://goo.gl/FwhPa3} (in Portuguese). Access: July 2016. Given the size of the organisation and its undisputed position as the leading crime syndicate in São Paulo, the figures are rather small. As a comparison, Mexico's Sinaloa Cartel profits about 3 billion dollars per year, a sum comparable to the annual earnings of Netflix or Facebook. See: \url{http://nyti.ms/1B09qyV}. Access: July 2016.} -- could have achieved such deep penetration into society and lowered the violence levels across all population groups in the whole state.
